Trends of downward SDR in Thessaloniki

### 2023-05-09 Article.Rmd
Commit 2023-05-09 11:17

Using the mean daily Global radiation we produce the trends of each data set, as departure from the seasonal value.

@@

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "Trends of daily means by sky conditions.")
```
\normalsize

@@

@@

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "Trends of daily means by sky conditions.")
```
\normalsize

>>>>

Using the mean daily Global radiation we produce the trends of each data set, as departure from the seasonal value.
Only for All-sky (Fig. \@ref(fig:trendALL)) and Cloudy-sky (Fig. \@ref(fig:trendCLOUD)) conditions the statistical significance of the trends is acceptable (Tab. \@ref(tab:trendtable)).

@@

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "\\label{tab:trendtable}Trends of daily means by sky conditions.")
# \\label{tab:tab2}
# knitr::kable(pp, caption = "Trends of daily means by sky conditions.")
```
\normalsize

@@

Similar we have produced the deseaonilised trend for different sky conditions for each season of the year, using the corresponding mean monthly values.

@@

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "\\label{tab:trendseasontable}Trends of daily means by sky conditions for the season of the year.")
```
\normalsize
